---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, 
                      comment = "##", 
                      fig.retina = 2, 
                      fig.path = "README_figs/README-")
```

[![Build Status](https://travis-ci.org/JohannesFriedrich/senseBox.svg?branch=master)](https://travis-ci.org/JohannesFriedrich/senseBox)
[![Build status](https://ci.appveyor.com/api/projects/status/oljck059k9io6qe7/branch/master?svg=true)](https://ci.appveyor.com/project/JohannesFriedrich/sensebox/branch/master)
[![Coverage Status](https://codecov.io/gh/JohannesFriedrich/senseBox/branch/master/graph/badge.svg)](https://codecov.io/gh/JohannesFriedrich/senseBox)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)


### Installation

```{r installation, eval=FALSE}
if(!require("devtools"))
  install.packages("devtools")
devtools::install_github("JohannesFriedrich/senseBox")
```

### Usage

Get some information about the senseBox project and list all senseBoxIds

```{r get_senseBox_stats}
library(senseBox)

stats <- get_senseBox_stats()
```


```{r, echo = FALSE}
knitr::kable(
  stats, format = "html"
)
```


```{r}
Id_list <- get_senseBox_Ids()
```

```{r echo = FALSE}
knitr::kable(
  head(Id_list),
  format = "html")
```


We chose one ID for the following examples

```{r set senseBoxId}
senseBoxId <- c("592ca4b851d3460011ea2635")
```

Show location of senseBox

```{r plot_location}
location <- get_senseBox_location(senseBoxId)

library(leaflet)
library(htmltools)

leaflet(location) %>%
  addProviderTiles(providers$OpenStreetMap) %>% 
  addTiles() %>%  
  addMarkers(~long, ~lat, popup = ~htmltools::htmlEscape(name))
```

Get some information about the senseBox sensors

```{r get_senseBox_sensor_info}
sensor_info <- get_senseBox_sensor_info(senseBoxId)
```

```{r print_sensor_info, echo = FALSE}
knitr::kable(
  sensor_info[[1]][,1:5],
  format = "html"
)
```


We can now download data from the senseBox, either from a specific sensorId or from all sensors within the sensBox.
In the following we are downloading all available sensors.

```{r}
data_all <- get_senseBox_data(senseBoxId)
```


When you are interested in just a selection of sensors, just submit the sensorIds to the function `get_senseBox_data()`.

```{r}
sensor_ids <- get_senseBox_sensor_Ids(senseBoxId)

data_sel <- get_senseBox_data(senseBoxId, 
                              sensorId = list(sensor_ids[[1]][1:2]))
```

When using the above code, by defatult, the data from the last 48 h will be downloaded. You can donwload up to 10,000 records and sepcify the date of the record. The maximum time frame for downloading data is back to one month from now.
Use the argument `fromDate` and `toDate` to specify the desired time frame. 

```{r}
data_timeframe <- get_senseBox_data(senseBoxId, 
                                    sensor_ids, 
                                    fromDate = "2017-11-11 11:11:11", 
                                    toDate = "2017-11-12 11:11:11")
```

Visualising the results from all sensors is one of the main aims and we recommend using the **R**-package `ggplot2`. 
We provide a sample code next and you just have to change the data executed in the function `melt()`.

```{r}
library(ggplot2)
library(reshape2)
library(scales)


data_melt <- melt(data_timeframe[[1]], id.vars = c("createdAt", "value"))

ggplot(data_melt, aes(x = createdAt, y = value, colour = L1)) +
  geom_line() +
  scale_x_datetime(labels = date_format("%H:%M", tz = Sys.timezone())) +
  facet_wrap(~L1, scales = "free") +
  theme(legend.position = "bottom",
        legend.title = element_blank())

```
